Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-04-01 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Update missing comments
Relecture globale et correction de coquilles

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and trained for NER on wikiner-fr.
\item \textbf{CamemBERT pre-trained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using approx. $845,000$ entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

To generate smaller training sets, we start from the initial training set and iteratively split it in half using the same stratified sampling strategy as for the train/dev split to maintain the relative frequency of directories. 
We stop if a directory has only one entry left, or if the current training subset contains less than 30 entries, maintaining the relative frequency of directories within it
Applying this procedure to the initial training set produces 8 training subsets containing 49, 99, 199, 398, 796, 1593, 3186, and 6373 entries.

@@

\subsection{Results and discussion}
Fig. \ref{fig:f1-vs-trainsize} displays the averaged precision, recall, and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: the performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the SpaCy model.

>>>>

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and trained for NER on wikiner-fr.
\item \textbf{CamemBERT pre-trained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modelling, using approx. $845,000$ entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

To generate smaller training sets, we start from the initial training set and iteratively split it in half using the same stratified sampling strategy as for the train/dev split to maintain the relative frequency of directories. 
We stop if a directory has only one entry left, or if the current training subset contains less than 30 entries, maintaining the relative frequency of directories within it.
Applying this procedure to the initial training set produces 8 training subsets containing 49, 99, 199, 398, 796, 1593, 3186, and 6373 entries.

@@

\subsection{Results and discussion}
\Cref{fig:f1-vs-trainsize} displays the averaged precision, recall, and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: the performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the SpaCy model.
